Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

If a regression is detected, the next step is to perform a critical path analysis by calculating the contribution of the critical path data trace from the regression period and will be compared with the critical path data derived from the baseline calculation. From this comparison, it will be sorted and the result of which operation has the largest latency change and becomes
strong candidate as the root cause of the regression.

>>>>

If a regression is detected, the next step is to perform a critical path analysis by calculating the contribution of the critical path data trace from the regression period and will be compared with the critical path data derived from the baseline calculation. From this comparison, it will be sorted and the result of which operation has the largest latency difference becomes strong candidate as the root cause of the regression.
